---
title: "mediaBabies"
output: rmarkdown::html_vignette
descrition: |
  The mediaBabies package allows you to explore the correlation between the   
  year a media title was released and the number of babies that were named    
  the corresponding character's name. This vignette introduces you to a       
  sample workflow and analysis.
vignette: >
  %\VignetteIndexEntry{mediaBabies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )
```

## Installation

You can install the development version of mediaBabies from
`[GitHub]` at https://github.com/burgerhaley97/mediaBabies.git with:

```{r, message = FALSE}
# Install the package from GitHub
devtools::install_github("burgerhaley97/mediaBabies")
```


## Introduction: 

The mediaBabies package allows you to explore the correlation between the year a media title was released and the number of babies that were named the corresponding character's name. This package uses media information from the IMDB developer data base and social security data for baby names counts from 1973 to 2023. You can use the custom functions in this package to filter the media and babies names data, create custom objects, and plot the objects to visualize any trends for specific names.

* `filter_char_by_baby_names()` Filters the movie character dataframe to only include movie characters that have a name listed in the baby names data frame.
* `filter_baby_names_by_char()` Filters baby names data frame to only include names
that have an associated character in the movie titles dataframe.
* `create_poi_df()` Creates a dataframe consisting of three columns: name, year, and
percent_change for the baby names data. 
* `create_media_names_df()` Creates a dataframe with the name, title, release_year, poi_year, and percent_change columns for future analysis.
* `infuences()` Creates a custom influence object for plotting.
* `baby_count()` Creates a custom baby count object for plotting.
  

## Example Workflow

```{r setup, message = FALSE}
library("mediaBabies")
```

We'll start by reading in and filtering the data included in our package. 
```{r}
# Load raw data media data
data(characters, package = "mediaBabies")

# Load female babies names data
data(female_babies, package = "mediaBabies")

# Filter the data frames so only matching names from each are kept.
babies_df <- filter_baby_names_by_char(female_babies, characters)
chars_df <- filter_char_by_baby_names(characters, female_babies)
head(chars_df)
```
Then we need to create our percent change data frame so we can identify years that are considered a point of interest. We then create the data frame representing names that are considered "media influenced." Here we choose to use the name Trinity.
```{r}
# percent change and point of interest functions
babies_pc_df <- create_percent_change_df(babies_df)
babies_poi <- create_poi_df(babies_pc_df)
head(babies_poi)

# create media influenced names table, use default max_range of 5  
media_influenced_df <- create_media_names_df(babies_poi, chars_df)
Trinity_influenced <- media_influenced_df[media_influenced_df$name == "Trinity", ]
head(Trinity_influenced)
```

Before plotting the results we need to convert the dataframes to custom objects. 
```{r}
# convert to custom influence object 
media_influence_object <- influences(Trinity_influenced)

# convert to custom baby_count object
babies_Trinity <- babies_df[["Trinity"]]
baby_count_obj <- baby_count("Trinity", as.numeric(1973), babies_Trinity)
```

Plot the custom objects from above to visualize the influence of media events on the name Trinity.
```{r,fig.dim = c(8,6)}
# plot and visualize the results 
plot(media_influence_object, baby_count_obj, sex = "female")
```

