---
title: "mediaBabies"
output: rmarkdown::html_vignette
descrition: |
  The mediaBabies package allows you to explore the correlation between the   
  year a media title was released and the number of babies that were named    
  the corresponding character's name. This vignette introduces you to a       
  sample workflow and analysis.
vignette: >
  %\VignetteIndexEntry{mediaBabies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

You can install the development version of mediaBabies from
[GitHub](https://github.com/burgerhaley97/mediaBabies.git) with:

```{r}
# You can install the package from GitHub
devtools::install_github("burgerhaley97/mediaBabies")
```


## Introduction: 

The mediaBabies package allows you to explore the correlation between the year a media title was released and the number of babies that were named the corresponding character's name. This package uses (insert data sources) to get the necessary media and baby names data. You can use the custom functions in this package to filter the raw media data and babies names data, create custom objects, and plot the objects to visualize any trends.

* `filter_char_by_baby_names()` Filters the movie character dataframe to only include movie characters that have a name listed in the baby names data frame.
* `filter_baby_names_by_char()` Filters baby names data frame to only include names
that have an associated character in the movie titles dataframe.
* `create_poi_df()` Creates a dataframe consisting of three columns: name, year, and
percent_change for the baby names data. 
* `media_influenced_names()` Creates a dataframe with the name, title, release_year, poi_year, and percent_change columns for future analysis.
  

## Example Workflow

```{r setup, message = FALSE}
# Make sure package is installed first 
library("mediaBabies")
```

We'll start by reading in and filtering the raw data.
```{r}
# load raw data media data
data(characters, package = "mediaBabies")
head(characters)

# load boy_names and girl_names
data(female_babies, package = "mediaBabies")
head(female_babies)

# Filter the data frames so only matching names from each are kept
babies_df <- filter_baby_names_by_char(female_babies, characters)
chars_df <- filter_char_by_baby_names(characters, female_babies)
```
Then we need to create our percent change data frame so we can identify years that are considered a point of interest. We then create the data frame representing names that are considered "media influenced." 
```{r}
# percent change and point of interest functions
babies_pc_df <- create_percent_change_df(babies_df)
babies_poi <- create_poi_df(babies_pc)

# create media influenced names table, use default max_range of 5 (specific name for data frame)
media_influenced_df <- create_media_names_df(babies_poi, chars_df)
name_influenced <- media_influenced_df[media_influenced_df$name == "Angela"]
```
Before plotting the results we need to convert the data frames to custom objects. 
```{r}
# convert to custom objects
media_influence_object <- influences(name_influenced_df)
babies_Angela <- baby_df[["Angela"]]
baby_count_object <- baby_count("Angela", 1973, babies_name_df)
```

Plot the custom objects from above to visualize the result 
```{r}
# plot and visualize the results 
# Update parameters once I see the plot functions and choose specific names
plot(media_influence)
plot(baby_counts)
plot(baby_pc_object)
```

